### 2015-05-22 writing/SNLI paper/corpus.tex
Assorted updates, new paper stats

\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l l} 
    \toprule
Training pairs &  550,153\\
Development pairs &  10,000\\
Test pairs & 10,000\\
\midrule
Premise mean token count & 14.1\\
Hypothesis mean token count & 8.3 \\
\midrule
Premise `S'-rooted parses & 74.0\%\\
Hypothesis `S'-rooted parses & 88.9\%\\
    \bottomrule
  \end{tabular}
% From 1.0rc3
\caption{\label{collection-stats}Key statistics for the raw sentence pairs. Since the two halves of each pair were collected separately, we report statistics for both.} 
\end{table}

\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l l} 
    \toprule
Validated pairs & 59,445\\
gold label $\ne$ original label & 8.4\%\\
Unanimous gold & 58.2\%\\
No gold (no 3 labels match) & 1.9\%\\
Label $=$ gold & 89.0\%\\
Label $=$ original author's label & 85.7\%\\
    \bottomrule
  \end{tabular}
    % From 1.0rc3
\caption{\label{validation-stats}Key statistics for the validated sentence pairs.} 
\end{table}

>>>>

\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l l} 
    \toprule
Training pairs &  550,152\\
Development pairs &  10,000\\
Test pairs & 10,000\\
\midrule
Premise mean token count & 14.1\\
Hypothesis mean token count & 8.3 \\
\midrule
Premise `S'-rooted parses & 74.0\%\\
Hypothesis `S'-rooted parses & 88.9\%\\
    \bottomrule
  \end{tabular}
% From 1.0rc3
\caption{\label{collection-stats}Key statistics for the raw sentence pairs. Since the two halves of each pair were collected separately, we report statistics for both.} 
\end{table}

\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l l} 
    \toprule
Validated pairs & 56,941\\
gold label $\ne$ original label & 6.8\%\\
Unanimous gold & 58.3\%\\
No gold (no 3 labels match) & 2.0\%\\
Label $=$ gold & 89.0\%\\
Label $=$ original author's label & 85.8\%\\
    \bottomrule
  \end{tabular}
    % From 1.0rc3
\caption{\label{validation-stats}Key statistics for the validated sentence pairs.} 
\end{table}
